---
title: "2021-03-17_Workbook-4"
author: "Emma"
date: "16/03/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Code to Run, include=FALSE}

library(tidyverse)
library(lubridate)
library(pmdplyr)
library(correlation)
library(ggraph)
library(patchwork)
library(dbplyr)

```

```{r Importing Data, include=FALSE}
# read data 
nz_0 <- readr::read_csv2(url("https://raw.githubusercontent.com/go-bayes/psych-447/main/data/nz/nz.csv"))

# to relevel kessler 6 variables
f<-c("None Of The Time","A Little Of The Time","Some Of The Time",  "Most Of The Time", "All Of The Time")

# get data into shape
nz <- nz_0 %>%
  dplyr::mutate_if(is.character, factor) %>%
  select(
    -c(
      SWB.Kessler01,
      SWB.Kessler02,
      SWB.Kessler03,
      SWB.Kessler04,
      SWB.Kessler05,
      SWB.Kessler06
    )
  ) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  mutate(FeelHopeless = forcats::fct_relevel(FeelHopeless, f)) %>%
  mutate(FeelDepressed = forcats::fct_relevel(FeelDepressed, f)) %>%
  mutate(FeelRestless = forcats::fct_relevel(FeelRestless, f)) %>%
  mutate(EverythingIsEffort = forcats::fct_relevel(EverythingIsEffort, f)) %>%
  mutate(FeelWorthless = forcats::fct_relevel(FeelWorthless, f)) %>%
  mutate(FeelNervous = forcats::fct_relevel(FeelNervous, f)) %>%
  dplyr::mutate(Wave = as.factor(Wave)) %>%
  dplyr::mutate(date = make_date(year = 2009, month = 6, day = 30) + TSCORE) 
```

Q1. Warmup
Using the nz dataset, make all the hours variables into integers

```{r Question 1}

#Q1. Changing variables into integers 

nz1 <- nz %>% 
  dplyr::mutate(
           Hours.Exercise = as.integer(Hours.Exercise),
           HLTH.SleepHours = as.integer(HLTH.SleepHours),
           Hours.Internet = as.integer(Hours.Internet),
           Hours.Work = as.integer(Hours.Work),
           Hours.News = as.integer(Hours.News),
           HoursCharity = as.integer(HoursCharity))
str(nz1)

#use str to check that they have been changed to integers. 

```

Q2a. Scale, center, transform
Create a new indicator that standardises the Pol.Orient variable, create a new indicator that centers the Pol.Orient variable, create a new indicator that centres the Age variable in decade-long units. Do this in a single piped workflow.

Print the head of the data frame so that we can see your work

```{r Question 2A}

NZ_2 <- nz%>% 
  select(Pol.Orient, Age)%>%
   mutate(Pol.Orient_S = scale(Pol.Orient, scale = TRUE, center  = TRUE))%>%
  #new indicator and centered variable 
         mutate(Age1 = scale(Age, scale = FALSE, center = TRUE)/10)
#new indicator that centers age in decade long units 
head(NZ_2)

#/10 divide by 10 to create decade. 
```

Q2b Data wrangle
Select Hour.Exercise and filter Wave 2019.

```{r Question 2B}

nz_4 <- nz%>% 
  select(Hours.Exercise, Wave)%>%
  mutate(Hours.Exercise_s = scale(Hours.Exercise, scale = TRUE, center = TRUE))%>%
      filter(Wave == "2019")

head(nz_4)
```


Q3. Working with dates
What are the maximum number of responses for a single day in 2018 and the maximum number of responses for a single day in 2019?

```{r Question 3}

# the below code prints a tible that lists max # responses in descending order. 
datrep5 <- nz %>%
  count(day = floor_date(date, "day"))%>%
  dplyr::mutate(Year = factor(ifelse(
    day < "2018-01-01",
    2017,
    ifelse(day < "2019-01-01", 2018,
           ifelse(day < "2020-01-01", 2019, 2020))
  ))) %>%
  arrange(day)

datrep5%>%
  arrange(desc(n))

# looking at the above tible the answers are: 
# max response for 2018 is 2018-06-21 (n=112)
# max responses for 2019 is 2019-12-03 (n=54)

```
Q4 Caculating dates and creating summaries
How many days are there between the date with the highest number of responses and the date with the second highest number of responses?

Information is pulled from the above summary. 

The date with the highest number of responses = 2018-06-21 (n=112)
The date with second highest number of responses =  2018-06-22 (n=93)

The days in between those two dates is one. 

To use a package could use = 

newvar <- lubridate::interval (ymd(""), ymd(""))
time_length (d, "day")


Bonus: 

The difference between the number of responses is =
```{r Q4}
112-93 

```
Q5. Working with date intervals
Suppose you were born on Dec 25, 1995 at 5.02:22 am Calculate your age in months on March 20,2021, at 1:22:04pm. 

```{r Q5}

# time between two dates in months

interval(ymd_hms("1995-12-25 05:02:22"), ymd_hms("2021-03-20 13:22:04")) %/% months(1) 

```
Q6 Create an ordered factor from numeric data
The Religion.Church variable contains responses to the question: “How many times each month do you attend church or religious service?”

Create factor with the following three levels:

People who attend church 0 times per month,
People who attend church 1-3 times per month,
People who attend church 4 or more times per month.
Make sure to re-level the factor so that the ordinal ranking moves from lowest to highest.


```{r Q6}
# cut function 

nz_5 <- nz %>% 
  dplyr::mutate(Religion.Church = cut(Religion.Church, 
                breaks = c(-Inf, 0, 4, Inf),
                labels = c("No Attendance", "Moderate Attendance", "High Attendance"), 
                right = TRUE
                ))
table(nz_5$Religion.Church, useNA = "ifany")
  
```


Q7.a Make a summary table
Using methods described in Lecture 4, create a table for average hours of sleep by month in the nz dataset

Q7.b Make a summary graph
Graph the average hours of sleep by month including 95% confidence intervals

Briefly explain why some intervals are wider than others.

```{r Q7a, warning=FALSE}
# arranging the date into month format

nz10 <- nz %>% 
  select(date, HLTH.SleepHours) %>%
  mutate(Months = month(date, label = TRUE)) %>% 
  group_by(Months) %>% 
  arrange(Months)


# the table 
library(kableExtra)
nz10 %>%
  select(HLTH.SleepHours, Months) %>%
  filter(!is.na(HLTH.SleepHours))%>%
  group_by(Months) %>%
  summarise(av_sleep = mean(HLTH.SleepHours, na.rm = T))%>%
  pivot_wider(names_from = Months, values_from = av_sleep) %>%
  kbl(caption = "Ave Hours Sleep by Month") %>%
  kable_classic_2(c("striped", "hover"), full_width = TRUE)%>%
  collapse_rows() 


# the summary graph 

nz10 %>%
  select(date, HLTH.SleepHours) %>%
  mutate(Months = month(date, label = TRUE)) %>%
  group_by(Months) %>%
  summarise(
    mn_sleep =  mean(HLTH.SleepHours, na.rm = TRUE),
    sd_sleep =  sd(HLTH.SleepHours, na.rm = TRUE),
    n_sleep = n()
  ) %>%
  mutate(
    se_sleep = sd_sleep / sqrt(n_sleep),
    lw_ci = mn_sleep - qt(1 - (0.05 / 2), n_sleep - 1) * se_sleep,
    up_ci = mn_sleep + qt(1 - (0.05 / 2), n_sleep - 1) * se_sleep
  ) %>%
  ggplot(., aes(x = Months, y = mn_sleep, colour = mn_sleep)) +
  geom_errorbar(aes(ymin = lw_ci, ymax = up_ci), width = .1) +
  geom_point(size = 3) +
  scale_y_continuous(limits = c(6,8)) + 
  theme_classic() + scale_fill_viridis_d()

  

```

Some intervals are wider than others in the above graph because there is more variation in the data for those months.  

Q8. Correlation graph
Created a correlation graph for the items in the Kessler 6 scale

These are FeelHopeless,FeelDepressed,FeelRestless,EverythingIsEffort,FeelWorthless,FeelNervous

```{r Q8, warning=FALSE}
# transform data 

corKes6 <- nz %>% 
  select(FeelHopeless,
         FeelDepressed,
         FeelRestless,
         EverythingIsEffort,
         FeelWorthless,
         FeelNervous, 
         KESSLER6sum
         ) %>%
  mutate_all(., as.integer) %>%
  mutate(KESSLER6sum = as.factor(KESSLER6sum),
         FeelNervous = log(FeelNervous + 1))

# correlation plot one  

library(correlation)
p1 <- corKes6 %>%
  correlation(partial = FALSE, multilevel = TRUE ) %>%
  plot()

# viewing the first plot 

corKes6 %>%
  correlation(partial = FALSE, multilevel = TRUE ) %>%
  summary()

# correlation plot two 

p2 <- corKes6 %>%
  select(-KESSLER6sum)%>% 
  correlation(partial = FALSE, multilevel = FALSE ) %>%
  plot()


corKes6 %>%
  select(-KESSLER6sum)%>% 
  correlation(partial = FALSE, multilevel = FALSE ) %>%
  summary()

# creating the correlation graph 

library(patchwork)
# create a two panel plot
p1 / p2 + 
  plot_annotation(title = "Plot of multilevel (a) and single-level (b) correlation", tag_levels = 'a') 

# tried to use this code: plot_layout(widths = c(2, 5), heights = c(5, 2)) to change the size of the correlations, but it would only make one more squished and the other a little fatter! 
  
```
What do you find most interesting about this plot?

The stronger correlations in Plot b are between feeling hopeless, worthless and depressed. These are all highly negative states, but I wonder why there aren't equally as strong correlations between them and EverythingIsEffort.  

Q9 Blank Papaja report is attached on blackboard. 

Q10 Patchwork
Use the patchwork library to create a figure with two plots on top of each other.

```{r Q10, warning=FALSE}
# two plots that are on top of each other using patchwork 

p3 <- ggplot(data = nz, aes(x = KESSLER6sum, y = FeelNervous, fill = FeelNervous)) + 
  geom_boxplot(notch=FALSE) + scale_fill_viridis_d() + 
  ggtitle('Feeling Nervous')
  

p4 <- ggplot(data = nz, aes(x = KESSLER6sum, y = FeelHopeless, fill = FeelHopeless)) + 
  geom_boxplot(notch=FALSE) + scale_fill_viridis_d() + 
  ggtitle('Feeling Hopeless')

p4_dims <- get_dim(p4)
p3_aligned <- set_dim(p3, p4_dims)
plot(p3_aligned)
plot(p4)

# code should make two plots that flash one on top of the other. Unsure if this is accurate as haven't been able to knit to PDF where it would show! 

```